\documentclass[a4paper,12pt,openany]{book}

% Essential packages for English document
\usepackage{fontspec}
\setmainfont{Amiri}
\newfontfamily\ipafont{Charis}
\usepackage{geometry}
\geometry{margin=2.0cm}
\usepackage{enumitem}
\usepackage{setspace}

% Spacing settings
\onehalfspacing
\setlength{\parskip}{0.2em}

% Remove blank pages before chapters
\let\cleardoublepage\clearpage

\begin{document}

% Title page
\begin{titlepage}
    \begin{center}
        \vspace*{1.5cm}
        {\Huge \textbf{Genyleap Whitepaper}} \\
        \vspace{0.5cm}
        {\Large Version 1.0} \\
        \vspace{0.5cm}
        {\large Publication Date: June 2025} \\
        \vspace{1.5cm}
        {\large High-Quality Software for a Better Life} \\
    \end{center}
    \vfill
\end{titlepage}

\chapter{Introduction}
At Genyleap, we envision a future where high-quality, powerful, and efficient digital technology serves everyone. We design simple and reliable software that enhances daily life, businesses, and innovation. Through open-source technologies and blockchain, we make advanced tools more accessible, strengthen transparency, and respect the environment with sustainable design. Genyleap delivers technology that is not only efficient but also inspiring and accessible to all.

\chapter{Cell Engine: The Core of Genyleap Technology}

The Cell Engine (\texttt{Cell}) is an advanced, open-source software system that forms the core of Genyleap's technological foundation. Built according to the \texttt{C++23} ISO/IEC 14882:2024 standard, it offers a modern framework for building high-quality, secure, and high-performance applications.

Designed for developers seeking full control, Cell empowers you to build anything—from desktop and mobile apps to web services, websites, and smart \texttt{IoT} devices—without relying on complex or expensive toolchains. It enables cost-efficient development without compromising performance or maintainability.

\textbf{Key Features:}
\begin{itemize}
    \item \textbf{Cross-Platform Compatibility:} Cell runs natively on desktop, mobile, embedded systems, and \texttt{WebAssembly}, enabling true portability across devices and operating systems.
    \item \textbf{Modular and Lightweight Architecture:} Its component-based structure allows for maximum customization and extensibility, while remaining lightweight and efficient.
    \item \textbf{Energy Efficiency:} Designed with sustainability in mind, Cell minimizes power consumption, supporting a greener and more environmentally conscious digital future.
    \item \textbf{High Performance \& Security:} Designed from the ground up for speed and safety, Cell delivers optimized execution with reliable and secure system behavior—ideal for modern applications that demand both responsiveness and resilience.
    \item \textbf{Globalization Support:} With multilingual features and internationalization support, Cell is ready for global deployment.
\end{itemize}

\footnote{The Cell Engine supports diverse project needs (multi-purpose), runs efficiently across platforms from desktops to \texttt{IoT} (cross-platform), and is designed for minimal energy use (green computing) to reduce its environmental footprint while delivering robust performance.}

\chapter{Vision and Strategies}

Genyleap redefines digital technology to empower developers, accelerate innovation, and foster sustainability in the software industry.

\begin{itemize}
    \item \textbf{High-Quality Software for All:} Genyleap’s tools are accessible, intuitive, and efficient—serving both everyday users and professional developers with robust, high-performance capabilities.
    \item \textbf{Business Empowerment:} Through powerful tools and expert consulting, Genyleap helps startups and enterprises transform ideas into successful, scalable solutions.
    \item \textbf{Environmental Sustainability:} Genyleap promotes green computing by designing low-power, high-efficiency software that aligns technological progress with ecological responsibility.
\end{itemize}

\footnote{Blockchain ensures verifiable, tamper-proof transaction records that strengthen digital trust and system integrity.}

\chapter{Geny Cryptocurrency (Token)}
\begin{quote}
We didn’t create a cryptocurrency... we created a gene! This is more than a token; it’s the DNA of interaction and creation in \texttt{Web3}.
\end{quote}
The GENY token, officially named \texttt{Genyleap}, is Genyleap’s digital currency, transforming our ecosystem into a dynamic, decentralized network. GENY is a “digital gene,” enabling individuals to create their identity and impact in \texttt{Web3}.
\begin{quote}
In every bit, a gene... in every gene, a world!
\end{quote}

\section*{Official Pronunciation}
In English, \textbf{GENY} is pronounced as \textit{``Jenny''} ({\ipafont /ˈdʒe.ni/}). The name derives from the fusion of “gene” and “why,” posing a conceptual question about the origin of creativity in the genetic structure of the digital world.

\section*{Technical Specifications of GENY}
\begin{itemize}
    \item \textbf{Token/Cryptocurrency Name}: \texttt{Genyleap}
    \item \textbf{Symbol}: \texttt{GENY}
    \item \textbf{Standard}: \texttt{ERC-20}
    \item \textbf{Total Supply}: 256,000,000 units
    \item \textbf{Burnable}: Yes (with restrictions defined by the team and \texttt{DAO})
    \item \textbf{Buyback}: Yes
    \item \textbf{Governance}: Via \texttt{Governor} smart contracts in \texttt{DAO}
\end{itemize}
\vspace{-0.5em}
\begin{quote}
Unleash your gene! The future belongs to those who shape their digital gene through thought and interaction.
\end{quote}
\newpage

\section*{Key Features and Audience of GENY}
\subsection*{Key Features}
GENY is designed to empower users, offering the following features:
\begin{itemize}
    \item \textbf{Service Access}: GENY is the key to using Genyleap products, such as Cell Engine-based applications.
    \item \textbf{Creative Rewards}: Users earn GENY for high-quality contributions (e.g., feedback, content, or software).
    \item \textbf{Digital Ownership}: GENY ensures secure ownership of digital assets (e.g., \texttt{NFTs}).
    \item \textbf{Fast Transactions}: Low-cost, instant payments within the ecosystem.
    \item \textbf{Decentralized Governance}: Voting in the \texttt{DAO} for project decisions.
    \item \textbf{Incentive Structure}: Rewards based on quality, not spam activities.
\end{itemize}
\begin{quote}
Just participate, and your digital gene takes shape!
\end{quote}
For example, a user can earn 0.25 GENY for providing feedback, or an artist can sell an \texttt{NFT} and receive 10 GENY as a reward.

\subsection*{Audience of GENY}
GENY is for all positive minds, not just developers or investors:
\begin{itemize}
    \item \textbf{General Users}: Access Genyleap apps and earn rewards for feedback.
    \item \textbf{Developers}: Build innovative software with the Cell Engine.
    \item \textbf{Artists}: Create and sell digital assets.
    \item \textbf{Startups}: Turn ideas into products with Genyleap support.
\end{itemize}
Every idea or contribution in Genyleap is valuable, and GENY connects you to the ecosystem.
\newpage

\section*{GENY Tokenomics}
GENY, with a total supply of 256 million units, is designed to ensure liquidity, growth, and sustainability. Token distribution is planned to encourage participation. The tables below detail allocation and vesting schedules.

\begin{table}[h]
\centering
\caption{GENY Token Allocation (Part 1)}
\small
\begin{tabular}{r c c c c c}
\hline
\textbf{Vesting} & \textbf{TGE (Million)} & \textbf{Percentage} & \textbf{Token Count (Million)} & \textbf{Category} & \textbf{Number} \\
\hline
48 months, 6-month cliff & 0 & 12.5 & 32 & Team and Core & 1 \\
36 months, 6-month cliff & 0 & 6.3 & 16 & Investors & 2 \\
24 months for 62 million & 2 & 25.0 & 64 & Ecosystem & 3 \\
Distribution by plan & 2 & 12.5 & 32 & GenyDrop & 4 \\
\hline
\end{tabular}
\end{table}

\begin{table}[h]
\centering
\caption{GENY Token Allocation (Part 2)}
\small
\begin{tabular}{r c c c c c}
\hline
\textbf{Vesting} & \textbf{TGE (Million)} & \textbf{Percentage} & \textbf{Token Count (Million)} & \textbf{Category} & \textbf{Number} \\
\hline
No vesting & 32 & 12.5 & 32 & Liquidity & 5 \\
24 months for 28 million & 4 & 12.5 & 32 & Treasury and \texttt{DAO} & 6 \\
24 months for 28 million & 4 & 12.5 & 32 & GenyLab & 7 \\
24 months, 3-month cliff & 0 & 6.3 & 16 & Growth Fund & 8 \\
\hline
-- & 44 & 100.0 & 256 & Total & -- \\
\hline
\end{tabular}
\end{table}

\textbf{Category Descriptions:}
\begin{enumerate}
    \item \textbf{Team and Core}: For project management and development.
    \item \textbf{Investors}: For initial financial support from strategic investors.
    \item \textbf{Ecosystem}: Rewards for users and developers contributing to services.
    \item \textbf{Airdrop}: Attracting new users through token tipping.
    \item \textbf{Liquidity}: Providing liquidity for exchanges and smooth trading.
    \item \textbf{Treasury and \texttt{DAO}}: Supporting decentralized decision-making and future development.
    \item \textbf{GenyLab}: Funding innovative projects and research.
    \item \textbf{Growth Fund}: Financing new projects and ecosystem expansion.
\end{enumerate}

\subsection*{Economic Details}
\begin{itemize}
    \item \textbf{Total Supply}: 256 million GENY tokens.
    \item \textbf{Initial Release (\texttt{TGE})}: 44 million tokens (17.2\%).
    \item \textbf{Token Buyback}: 15\% of project profits used for buybacks and transfer to \texttt{buybackPool}.
    \item \textbf{Token Burning}: Up to 2\% of circulating supply burned annually in crisis scenarios (e.g., hacks or very lower price).
\end{itemize}
\newpage

\section*{GENY Units and Subunits}
At Genyleap, we believe true value lies in the smallest units, not in billions of ineffective tokens. Our ecosystem is built on international unit standards (\texttt{SI}) and a binary system (powers of 2), ensuring precision and transparency at all levels. This intelligent structure, especially in reward systems and microtransactions, delivers a simple, accurate, and unique experience, where every interaction, like a singular gene, carries value, meaning, and creation.
\begin{quote}
Every interaction, a unique gene! GENY brings an unparalleled sense of creation and value.
\end{quote}
GENY is the primary unit of value, using binary prefixes like kibi (\texttt{Ki}) and mebi (\texttt{Mi}) to maintain computational precision across all scales. This system provides a robust foundation for interactions, from microtransactions to large-scale projects—transparent, engineered, and forward-looking.

\subsection*{GENY Units Table}
\begin{table}[h]
\centering
\caption{GENY Subunits}
\small
\begin{tabular}{l c c r}
\hline
\textbf{Prefix} & \textbf{Symbol} & \textbf{Amount in GENY} & \textbf{Amount in \texttt{sub unit}} \\
\hline
Mebi (\texttt{MebiGENY}) & \texttt{MiGENY} & 1,048,576 & 268,435,456 \\
Kibi (\texttt{KibiGENY}) & \texttt{KiGENY} & 1,024 & 262,144 \\
-- & \texttt{GENY} & 1 & 256 \\
Milli (\texttt{MilliGENY}) & \texttt{mGENY} & 0.001 & 0.000256 \\
Micro (\texttt{MicroGENY}) & \texttt{\textmu GENY} & 0.000001 & 0.000000256 \\
Nano (\texttt{NanoGENY}) & \texttt{nGENY} & 0.000000001 & 0.000000000256 \\
Pico (\texttt{PicoGENY}) & \texttt{pGENY} & 0.000000000001 & 0.000000000000256 \\
\hline
\end{tabular}
\end{table}

\subsection*{Power-of-Two Scaling}
We use binary conversions (powers of 2, e.g., 1,024 instead of 1,000) to ensure digital computation accuracy. For example, 1 \texttt{KiGENY} equals 1,024 GENY, not 1,000 GENY. This standard, common in computer science for memory, processing, and data transfer, prevents rounding errors in microtransactions (e.g., \texttt{IoT} sensors or data analytics). This precision makes GENY ideal for advanced applications.

\subsection*{Applications of GENY and GEN}
Instead of billions of tokens, we use milli, micro, and nano units for small interactions and kibi and mebi for large projects. This approach enhances simplicity and appeal in the Genyleap ecosystem, particularly in tipping systems that create delightful and meaningful experiences.
\begin{itemize}
    \item \textbf{Microtransactions}: \texttt{IoT} sensors transmit environmental data with 0.000000001 GENY.
    \item \textbf{Social Tipping}: 0.1 GENY to support a creative post.
    \item \textbf{Subscriptions}: Activate a premium subscription with 10 GENY.
    \item \textbf{Major Contributions}: Allocate 2,000,000 GENY via \texttt{DAO} for community projects.
\end{itemize}

\textbf{Usage Examples:}
\begin{table}[h]
\centering
\caption{Usage Examples for GENY and \texttt{GEN}}
\small
\begin{tabular}{l c r}
\hline
\textbf{Scenario} & \textbf{Equivalent in GENY} & \textbf{Amount in \texttt{GEN}} \\
\hline
Large \texttt{DAO} Grant & 2,000,000 & 512,000,000 \\
Liquidity Injection & 500,000 & 128,000,000 \\
Premium Subscription & 10 & 2,560 \\
Feature Unlock & 1 & 256 \\
Large Tip & 0.5 & 128 \\
Small Tip & 0.1 & 25.6 \\
Microservice Call & 0.01 & 2.56 \\
Data Analytics Request & 0.0001 & 0.0256 \\
\texttt{IoT} Sensor Ping & 0.000000001 & 0.000000256 \\
\hline
\end{tabular}
\end{table}

\subsection*{Engaging Applications}
\begin{itemize}
    \item \textbf{\texttt{IoT} Microtransactions}: Sensors transmit environmental data with 0.000000001 GENY.
    \item \textbf{Creative Tipping}: 0.1 GENY to support digital content, like an inspiring post.
    \item \textbf{Dynamic Governance}: Voting in \texttt{DAO} with 1,000 GENY for major projects.
    \item \textbf{Micro-Economy}: Businesses offer digital services with 0.01 GENY.
\end{itemize}

\chapter{Genyleap Audience}
Genyleap creates value for the following groups:
\begin{itemize}
    \item \textbf{General Users}: Access to practical tools for daily tasks.
    \item \textbf{Developers}: A platform for building innovative software.
    \item \textbf{Artists}: Creating and selling digital assets with dedicated tokens.
    \item \textbf{Startups}: Support for turning ideas into products.
    \item \textbf{Organizations}: Customized solutions for businesses.
\end{itemize}

\chapter{Genyleap Vision}
Genyleap builds a future where digital software is high-quality, simple, and sustainable. With open-source technologies, blockchain, and \texttt{DAO}, we provide universal access to technology, creating a world where software enhances life.

\chapter{Call to Collaboration}
Genyleap invites developers, artists, startups, and investors to join us on this innovative journey. For more information, visit genyleap.com or connect with us on social media.

\section*{GENY Smart Contract Addresses}
GENY smart contracts are deployed on the Ethereum blockchain and utilize the \LRE{UUPS} proxy architecture to manage transactions, token allocation, and decentralized governance of the Genyleap ecosystem. The \texttt{Multi-Sig} contract, with a three-signature structure, ensures greater security and transparency. To view contract details, check the addresses on \texttt{basescan.org}:

\begin{table}[h]
\centering
\caption*{Main GENY Contracts}
\small
\begin{tabular}{c r}
\hline
\textbf{Contract Name} & \textbf{Contract Address} \\
\hline
\texttt{GenyToken} & {\texttt{0x2a3d6f8c1fc4AcDcf3A75d19b445bae02F03676B}} \\
\texttt{GenyAllocation (Proxy)} & {\texttt{0xEeef3EFb77C72aC202BFfd7AFE123e9b86c15360}} \\
\texttt{Multi-Sig} & {\texttt{0x1a0819A7412BbFed6322C8B498aa58E3BD4d53B4}} \\
\texttt{Deployer} & {\texttt{0x477A5692e3D72a15eC3657A66F1F0bE67dAEA8B1}} \\
\hline
\end{tabular}
\end{table}

\section*{References and Addresses}

\begin{enumerate}
    \item \textbf{Basescan}: \texttt{https://basescan.org/token/0x2a3d6f8c1fc4AcDcf3A75d19b445bae02F03676B}
    \item \textbf{Source Address}: \texttt{https://github.com/genyleap/geny-token}
\end{enumerate}

\end{document}
